Data Exercise

### 2024-06-28 docs/Data-Exercise/data-exercise.qmd
All key files should be in docs/data exercise/data-exercise

Placeholder file for the future data exercise.

@@

```{r}
# Write to Excel file
write_xlsx(as.data.frame(applicant_final), "Employee_Selection_Scores.xlsx")
```

@@

\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\Conclusion*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*

>>>>

Placeholder file for the future R coding exercise.

@@

```{r}
# Write to Excel file
#write_xlsx(as.data.frame(applicant_final), "Employee_Selection_Scores.xlsx")
```

@@
